---
title: 'Homework #5'
author: "Cory Roth"
date: "3/06/2023"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chocolate

1.  What is the overall number of chocolate bars rated?

    ```{r}
    library(ggplot2)
    choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
    #head(choco)

    str(choco)

    ```

    There was 1852 chochlate bars rated

2.  How does the number of ratings depend on the year? Draw a bar chart
    of the number of reports.

    ```{r}
    ggplot(choco, aes(Rating))+
      geom_bar()+
      facet_wrap(.~Review.Date)

    ```

3.  For each of the questions below provide at least one graphic as a
    basis for your answer.

    1.  How are ratings distributed? Draw a histogram of ratings and
        describe it. Don't forget to mention outliers, if there are any.

```{r}
ggplot(choco, aes(Rating))+
  geom_histogram()
```

The Ratings are on a 5 points scale. Most Ratings are between 2.5-4.
There are very few ratings that a perfect 5 and very few that are the
worst score being a 1

    2.  Do ratings depend on the cocoa percentage of a chocolate bar?

```{r}
ggplot(choco, aes(Rating, Cocoa.Pct))+
  geom_jitter()
```

There does not seem to be a correlation between cocoa percentage and
ratings. Looking at the graph above, the ratings are not depeneanded on
cocoa.Pct 3. How do ratings compare across different company locations?
Focus on the three locations with the most ratings:

```{r}
 top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(top3, aes(Rating))+
  geom_bar()+
  facet_wrap(.~Company.Location)
```

Canada's and France's Average Rating is between 3-4, whereas the USA has
a lot more chocolate bars under the 3 rating, meaning the USA overall
rating would be lower than Canada and France <!-- -->

        top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

Upload your answers to the repository. Discuss and refine answers as a
team.

YOUR OWN QUESTION? 2. How does the number of ratings depend on the
Company in France?


```{r}
 topF <- dplyr::filter(choco, Company.Location %in% c( "France"))

 ggplot(topF, aes(Rating))+
      geom_bar()+
  facet_wrap(.~Company)
      

```
It looks like certain companies like Bonnat and Valrhona get higher average ratings on their chocolate than companies like A.Morin and Lai aka Chat-Noir.